Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-09-01 doc/main_jfm.tex

\begin{figure}
\centering
\includegraphics[width=0.32\textwidth]{PermPanelB.pdf}
\includegraphics[width=0.32\textwidth]{PermPanelC.pdf}
\includegraphics[width=0.32\textwidth]{PermPanelA.pdf}
  \caption{\label{figure:permeability} JP vesicles are suspended in a
  quiescent flow for relaxations where the reference arc lengths $L_0$
  are $107$ nm, $218$ nm, and $141$ nm with particle diameters $2.5$ nm,
  $2.5$ nm, and $1.25$ nm, respectively. (a) The arc length $L$
  decreases over time where the dashed curves represent the data and
  solid curves are linear fits; (b) A linear relationship between
  $R\Delta p$ and the relative difference $L/L_0-1$; (c) A linear
  relationship between aqueous flux $dA/dt$ and $L\Delta p$. For panels
  (b) and (c), the cross and asterisk symbols are numerical results and
  fitted by using solid lines.}
\end{figure}

The particles in our setup do not abut but rather have small gaps due to
repulsive forces.  The gaps allow for some fluid flux across the JP
bilayer.  In membrane mechanics, aqueous flux is quantified the equation
\begin{equation} \label{eq:perm} \frac{dA}{dt} = -P  L \Delta p.
\end{equation} where $P$ is a hydraulic permeability constant
\cite{CHABANON, qua-gan-you2021}.

The JP vesicle data is in complete agreement with the continuum
mechanical model~\eqref{eq:stretch}-\eqref{eq:perm_solution}.  In
Figure~\ref{figure:permeability}, we considered three configurations: a
configuration with 58 particles ($L_0 = 107$ nm, plus symbols); a
configuration with 119 particles ($L_0 = 218$ nm, asterick symbols); and
finally a configuration with 117 particles but with diameter 1.25 nm
rather than the usual 2.5 nm ($L_0 = 141$ nm, times symbols).  Here $A$
and $L$ refer to the area and length of the mid plane curve separating
the inner and outer monolayers.  (The values for $L_0$ are the
asymptotic values for $L$ in Figure \ref{figure:permeability}c).

Figure~\ref{figure:permeability}a plots the data for the Laplace
pressure relationship \eqref{eq:LaplacePressure}.  The pressure jump
$\Delta p$ is the pressure at the particle center minus the far-field
pressure (see Figure~\ref{figure2}c,d), $R = L/2\pi$ is the vesicle
radius, and the horizontal axis is for the relative stretch. The solid
lines are linear fits, showing that for circular JP vesicles, $R\Delta
P$ is basically proportional to relative stretching $L/L_0 - 1$ . The
proportionality constant is the same for the 58 and 119 particle cases
where the diameters are the same, suggesting that the stretching modulus
$K_A$ of JP bilayers is independent of the number of particles. The 117
particle case had diameters 1.25 nm and this data set gave a smaller
stretching modulus  $K_A = 102$ pN nm$^{-1}$.  The interpretation is
that changes to particle size, while keeping $\rho$, $M$, and $\rho_0$
fixed, lead to different physical properties.

Furthermore, Figure~\ref{figure:permeability}b and shows that $L\Delta
P$ is proportional to $\frac{dA}{dt}$ in accord with \eqref{eq:perm}.
The slopes of the linear fits give the hydraulic permeability
coefficient $P.$ The data provide $P = 0.0296$ nm$^3$ ns$^{-1}$
pN$^{-1}$ and $P = 0.0283$ nm$^3$ ns$^{-1}$ pN$^{-1}$ for the 58 and 119
particle cases, respectively.  These values suggest that the JP bilayer
permeability is independent of particle number, as was the case for the
stretching modulus.  The permeability for the 117 particle number case
was larger, 0.0566 nm$^3$ ns$^{-1}$ pN$^{-1}$.  That is because
hydrophobic attraction vanishes with particle size, leading to larger
gaps between the particles for the same repulsion.  The hydraulic
permeability we calculate, however, is not in agreement with
experimentally derived values and is larger by a few orders of
magnitude. This discrepancy is perhaps due to inter-particle distance of
the JP being relatively large to the inter-molecular spacing of lipids
in real bilayers.  In future studies, we can test this hypothesis be
changing the repulsion strength and length for example.

Since the vesicles in Figure~\ref{figure2}a are nearly we circular, we
can combine~\eqref{eq:stretch},~\eqref{eq:LaplacePressure},
and~\eqref{eq:perm}, to derive  
\begin{align}
\label{eq:perm_solution}
L_0(L-L(0)) + L_0^2 \ln\left|\frac{L-L_0}{L(0)-L_0}\right| = -4\pi^2 P K_A t.
\end{align}
The theoretical time courses for \eqref{eq:perm_solution} are in good
quantitative agreement with the JP data for
(Figure~\ref{figure:permeability}c).

>>>>

\begin{figure}
\centering
  \todo[inline]{The left figure is shorter than the other 2}
\includegraphics[width=0.32\textwidth]{PermPanelB.pdf}
\includegraphics[width=0.32\textwidth]{PermPanelC.pdf}
\includegraphics[width=0.32\textwidth]{PermPanelA.pdf}
  \caption{\label{figure:permeability} JP vesicles are suspended in a
  quiescent flow for relaxations where the reference arc lengths $L_0$
  are $107$ nm, $218$ nm, and $141$ nm with particle diameters $2.5$ nm,
  $2.5$ nm, and $1.25$ nm, respectively. (a) The arc length $L$
  decreases over time where the dashed curves represent the data and
  solid curves are linear fits; (b) A linear relationship between
  $R\Delta p$ and the relative difference $L/L_0-1$; (c) A linear
  relationship between aqueous flux $dA/dt$ and $L\Delta p$. For panels
  (b) and (c), the cross and asterisk symbols are numerical results and
  fitted by using solid lines.}
\end{figure}

The particles in our setup do not abut but rather have small gaps due to
repulsive forces.  The gaps allow for some fluid flux across the JP
bilayer.  In membrane mechanics, aqueous flux is quantified the equation
\begin{align}
  \label{eq:perm} 
  \frac{dA}{dt} = -P  L \Delta p,
\end{align}
where $P$ is a hydraulic permeability constant \cite{CHABANON,
qua-gan-you2021}.

The JP vesicle data is in complete agreement with the continuum
mechanical model~\eqref{eq:stretch}--\eqref{eq:perm}. In
Figure~\ref{figure:permeability}, we considered three configurations: a
configuration with 58 particles ($L_0 = 107$ nm, plus symbols); a
configuration with 119 particles ($L_0 = 218$ nm, asterisk symbols); and
finally a configuration with 117 particles but with diameter 1.25 nm
rather than the usual 2.5 nm ($L_0 = 141$ nm, times symbols). Here $A$
and $L$ refer to the area and length of the mid plane curve separating
the inner and outer monolayers. The values for $L_0$ are the asymptotic
values for $L$ in Figure~\ref{figure:permeability}c.

Figure~\ref{figure:permeability}a plots the data for the Laplace
pressure relationship \eqref{eq:LaplacePressure}. The pressure jump
$\Delta p$ is the pressure at the particle center minus the far-field
pressure (see Figures~\ref{figure2}c and~\ref{figure2}d), $R = L/2\pi$
is the vesicle radius, and the horizontal axis is the relative stretch.
The solid lines are linear fits, showing that for circular JP vesicles,
$R\Delta P$ is essentially proportional to the relative stretching
$L/L_0 - 1$. The proportionality constant is the same for the 58 and 119
particle cases where the diameters are the same, suggesting that the
stretching modulus $K_A$ of JP bilayers is independent of the number of
particles. The 117 particle case had diameters 1.25 nm and this data set
results in a smaller stretching modulus of $K_A = 102$~pN~nm$^{-1}$. The
interpretation is that changes to particle size, while keeping $\rho$,
$M$, and $\rho_0$ fixed, lead to different physical properties.

Furthermore, Figure~\ref{figure:permeability}b and shows that $L\Delta
P$ is proportional to $\frac{dA}{dt}$ in accord with \eqref{eq:perm}.
The slopes of the linear fits give the hydraulic permeability
coefficient $P$. The data provide $P = 0.0296$ nm$^3$ ns$^{-1}$
pN$^{-1}$ and $P = 0.0283$ nm$^3$ ns$^{-1}$ pN$^{-1}$ for the 58 and 119
particle cases, respectively. These values suggest that the JP bilayer
permeability is independent of particle number, as was the case for the
stretching modulus. The permeability for the 117 particle number is
0.0566 nm$^3$~ns$^{-1}$~pN$^{-1}$. The increase in the permeability is
caused by the hydrophobic attraction vanishing with particle size,
leading to larger gaps between the particles for the same repulsion. The
hydraulic permeability we calculate, however, is not in agreement with
experimentally derived values and is larger by a few orders of
magnitude. This discrepancy is perhaps due to inter-particle distance of
the JP being relatively large to the inter-molecular spacing of lipids
in real bilayers. In future studies, we can test this hypothesis be
changing the repulsion strength and length for example.

Since the vesicles in Figure~\ref{figure2}a are nearly circular, we can
combine~\eqref{eq:stretch},~\eqref{eq:LaplacePressure},
and~\eqref{eq:perm}, to derive
\begin{align}
\label{eq:perm_solution}
L_0(L-L(0)) + L_0^2 \ln\left|\frac{L-L_0}{L(0)-L_0}\right| = -4\pi^2 P K_A t.
\end{align}
The theoretical time courses for \eqref{eq:perm_solution} are in good
quantitative agreement with the JP data for
(Figure~\ref{figure:permeability}c).
